Sorting algorithms: how are they affected by memory faults?

### 2019-12-21 paper/MaterialsAndMethods.tex
finalização do experimental setup

>>>>

We use Python libraries to make data analysis and plot graphs. These libraries were:
\begin{itemize}
    \item \textit{Pandas\footnote{https://pandas.pydata.org}}: open source library providing data structures and data analysis tools;
    \item \textit{NumPy\footnote{https://numpy.org}}: library for scientific computing with Python;
    \item \textit{SciPy\footnote{https://www.scipy.org}}: ecosystem of open-source software for mathematics, science, and engineering;
    \item \textit{StatsModels\footnote{https://www.statsmodels.org}}: module that provides classes and functions for the estimation of many different statistical models, as well as for conducting statistical tests, and statistical data exploration;
    \item \textit{Matplotlib\footnote{https://matplotlib.org}}: plotting library;
    \item \textit{Seaborn\footnote{https://seaborn.pydata.org}}: data visualization library based on matplotlib.
\end{itemize}
